Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-04-15 thesis-main.tex
Stop forcing PDF output
Comment out completely outdated sections
Prepare alternative \includeonly statements
Add lists of figures and tables after ToC
Number figures and tables together
Also, order them together.
Drop unused package fixfoot

% Ensure that arXiv processes this as PDF.
\pdfoutput=1

@@

\title{Optimizing and Incrementalizing Collection Queries by AST Transformations}
\author{Paolo G. Giarrusso}

% Only for development.
%
% Requires that other files are compiled with include, and can only be used in
% incremental runs: a first run has to be made without includeonly.
%
% \includeonly{pldi14/sec-preliminaries,pldi14/sec-intro}
%
% Also, include can add extra page breaks, so maybe switch back to input at the end.
% From http://web.science.mq.edu.au/~rdale/resources/writingnotes/latexstruct.html.
\begin{document}
\maketitle
\input{pldi14/agda}

@@

@@

% Include either-or, one includes the other.
%\include{change-theory-reconstruct}
\include{pldi14/sec-change-theory}
\include{pldi14/sec-change-equiv}

\DeclareFixedFootnote{\EmptyEmptyNote}{%
To evaluate a closed term $t$, we need no environment entries, so
the empty environment $\EmptyEnv$ suffices:
$\EvalWith*{t}{\EmptyEnv}$ is the value of $t$ in the empty environment, and
$\;\EvalIncSmashWith*{t}{\EmptyEnv}{\EmptyEnv}$
is the value of $t$ using the change semantics, the empty environment and the empty change
environment.}

\include{pldi14/sec-differentiate}
\include{pldi14/sec-practice}
\include{pldi14/sec-concl}

>>>>

@@

% Number floats and figures together. Documented at
% http://stackoverflow.com/a/43266057/53974.
\makeatletter
\let\c@table\c@figure
\let\ftype@table\ftype@figure
\makeatother
\title{Optimizing and Incrementalizing Collection Queries by AST Transformations}
\author{Paolo G. Giarrusso}

% Only for development.
%
% Requires that other files are compiled with include, and can only be used in
% incremental runs: a first run has to be made without includeonly.
%
%\includeonly{pldi14/sec-preliminaries,pldi14/sec-intro}
%\includeonly{pldi14/sec-intro}
%
% Also, include can add extra page breaks, so maybe switch back to input at the end.
% From http://web.science.mq.edu.au/~rdale/resources/writingnotes/latexstruct.html.
\begin{document}
\maketitle
\input{pldi14/agda}

@@

\listoffigures
\listoftables

@@

% Include either-or, one includes the other.
%\include{change-theory-reconstruct}
%\include{pldi14/sec-change-theory}
\include{pldi14/sec-change-equiv}

%\include{pldi14/sec-differentiate}
\include{pldi14/sec-practice}
\include{pldi14/sec-concl}
